Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-07 Latex Source/paper.tex
abstract done

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass[sigconf]{acmart}
% part of the template 
\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

% packages that I added
\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}
% \usepackage[section]{placeins} %% used to keep the images in the section that I want them in

@@

\begin{abstract}
A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
and typing efficiency. A participant would take a typing test and qunatified behavioral test (QBTest) with three conditions.
The condiditons would be instrumental music, lyrical music, and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
a type of eye tracker, will track the participants eye movements.
Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818. 
% add results from two tests together
\end{abstract}

>>>>

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side

% part of the template 
\AtBeginDocument{%
  \providecommand\BibTeX{{%  
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

@@

% packages that I added
\usepackage{graphicx} %% For pictures
\graphicspath{{./pics/}}

@@

\begin{abstract}
A two-part test was conducted to determine if there was a correlation between the effectivness of music versus no music on cognitive response time
and typing efficiency. A participant would take a typing test and quantified behavioral test (QBTest) with three conditions.
The condiditons would be instrumental music (music with no lyrics), lyrical music (music with lyrics), and lastly no music. While the participant takes the QBTest, the EyeWriter 2.0,
a type of eye tracker, will track the participants eye movements.
Individually the two test were not statistically significant. The typing test's \textit{p} value was 0.1172 whereas the QBTest's \textit{p} value was 0.0818 when ran through ANOVA. There was correlation between the effectiveness of the two on response time. This 
can be seen in a heat map of eye movements that is generated from the EyeWriter when inputted into GISPro, a program that analyses geographic information systems which a heatmap is considered.
% please verify the last line
\end{abstract}
